Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-23 methods_paper/fabl-paper.tex
update.

\paragraph{Directly Modeling the Data} Instead of relying on comparison vectors, some authors will incorporate the data directly into their bipartite record linkage model \citep{Fortinietal01, Matsakis10, liseo_jos_2011, liseo_2011, gutman_bayesian_2013, shan2020bayesian}. These approaches have led to extensions regarding downstream tasks in the literature or joint models, such as regression approaches \citep{dalzell2018regression, steorts2018generalized, tancredi2020unified}.

There have been extensions to directly model the data in this literature at combining many databases, however, we do not review this as it's not directly comparable with the situation of bipartite record linkage \citep{steorts_bayesian_2016, steorts_entity_2015, zanella_flexible_2016, marchant_distributed_2019, tancredi_2015_regression, }.

\paragraph{Classification Approaches}

\textcolor{red}{Now state the related work here in this literature and common approaches.}

\textcolor{red}{ATTN: These are just notes and need to be edited}

\begin{enumerate}
\item The most common approach is FS. 
\item ``A number of approaches directly model the information contained in the datafiles (Fortini et al., 2002; Matsakis, 2010; Liseo and Tancredi, 2011; Tancredi and Liseo, 2011; Gutman et al., 2013; Steorts et al., 2013), which requires crafting specific models for each type of field in the datafile, and are therefore currently limited to handle nominal categorical
fields, or continuous variables modeled under normality." [Update this literature] 
\item Classification. ``A more common way of tackling this problem is to see it as a traditional classification
problem: we need to classify record pairs into matches and non-matches. If we have access
to a sample of record pairs for which the true matching statuses are known, we can train a
classifier on this sample using comparisons between the pairs of records as our predictors,
and then predict the matching statuses of the remaining record pairs (e.g., Cochinwala et al.,
2001; Bilenko et al., 2003; Christen, 2008; Ventura et al., 2013)." [Update this literature] 
\end{enumerate}

>>>>

\paragraph{Directly Modeling the Data} Instead of relying on comparison vectors, some authors will incorporate the data directly into their bipartite record linkage model \citep{Fortinietal01, Matsakis10, liseo_jos_2011, liseo_2011, gutman_bayesian_2013, shan2020bayesian}. These approaches have led to extensions regarding downstream tasks in the literature or joint models, such as regression approaches \citep{dalzell2018regression, steorts2018generalized, tancredi2020unified}.  There have been extensions to directly model the data in this literature where authors consider merging multiple databases (more than two) \citep{steorts_bayesian_2016, steorts_entity_2015, zanella_flexible_2016, marchant_distributed_2019, tancredi_2015_regression}. 
We do not review this literature given that it is not directly/fairly comparable with the case of bipartite record linkage.

\paragraph{Classification Approaches} 
One common way of approaching the record linkage task, especially in computer science and machine learning is using a classification approach. One uses a model (such as random forests) to classify records into matches/non-matches. When access to unique identifiers is available, one can create a training data (or reference data) set of record pairs (where the true match status is known).  Finally, one can train a classifier using the reference data set to predict the match status on any record pairs that were not included in the reference data set \citep{Bilenko2006, Christen2008, ventura2015seeing}.
